Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement

### 2020-12-21 vesicle_code/docs/permeableVes/main.tex
another note about flow rate
added a few todos

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Quiescent Flow} 
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/relaxationComposite.tikz}
  \else
  \includegraphics{figures/relaxationComposite.pdf}
  \fi
  \caption{\label{fig:relaxationComposite} (a): Snapshots of four
  semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
  quiescent flow. The fluid flux along the red regions is into the
  vesicle, and the fluid flux along the blue regions is out of the
  vesicle. In all cases, the vesicle reaches a steady state circular
  shape. (b): The reduced area of each of the simulations. The
  particular snapshots in (a) occur at the marks along the curve.}
\end{figure*}

@@

Our simulations indicate the
semi-permeability does affect the excess pressure, and the vesicle's
reduced area reduces by about 6.1\%
(Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
a constant rate we expect that a larger amounts of deflation is possible
if the vesicle is stenosed for a longer period of time. Therefore, in
Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
through a channel of double the length, and we observe that the reduced area
decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).

@@

\begin{itemize}
  \item Vesicle velocity in plot (a) varies from 5 to 24 microns/s
  \item Vesicle velocity in plot (b) varies from 5 to 28 microns/s
  \item Vesicle velocity in plot (c) varies from 0.2 to 2 microns/s
  \item Vesicle velocity in plot (d) varies from 5 to 25 microns/s
  \item Vesicle velocity in plot (g) varies from 14 to 95 microns/s (see
    plot (i))
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Quiescent Flow} 
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/relaxationComposite.tikz}
  \else
  \includegraphics{figures/relaxationComposite.pdf}
  \fi
  \caption{\label{fig:relaxationComposite} (a): Snapshots of four
  semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
  quiescent flow. The fluid flux along the red regions is into the
  vesicle, and the fluid flux along the blue regions is out of the
  vesicle. In all cases, the vesicle reaches a steady state circular
  shape. (b): The reduced area of each of the simulations. The
  particular snapshots in (a) occur at the marks along the curve.}
\end{figure*}
\todo[inline]{put a vertical dashed line at the times when permeability
starts to be important. Convert to physical time.}

@@

Our simulations indicate the semi-permeability does affect the excess
pressure, and the vesicle's reduced area reduces by about 6.1\%
(Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
a constant rate we expect that a larger amounts of deflation is possible
if the vesicle is stenosed for a longer period of time. Therefore, in
Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
through a channel of double the length, and we observe that the reduced
area decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
\todo[inline]{This example also used a smaller flow rate of $8.4\mu$m/s}
\todo[inline]{Membrane tension. Look at each of the five cases and find
the instance where tension reaches its max value. Plot the tension as
the colorbar along the vesicle shape.}

@@

\begin{itemize}
  \item Vesicle velocity in plot (a) varies from 5 to 24 microns/s
  \item Vesicle velocity in plot (b) varies from 5 to 28 microns/s
  \item Vesicle velocity in plot (c) varies from 0.2 to 2 microns/s
  \item Vesicle velocity in plot (d) varies from 5 to 25 microns/s
  \item Vesicle velocity in plot (g) varies from 14 to 95 microns/s (see
    plot (i))
\end{itemize}
\todo[inline]{Center of mass vs.~time}
\todo[inline]{Membrane tension. Look at each of the five cases and find
the instance where tension reaches its max value. Plot the tension as
the colorbar along the vesicle shape.}
